---
title: "Chapter_5_GFG"
output: 
  html_document: 
    keep_md: yes
date: "2022-11-28"
---

## 5.1. QUIZ

1. 

2.

3.

## EXERCISES

# 5.2. Choices

1.

```{r}
ifelse(TRUE, 1, "no")
ifelse(FALSE, 1, "no")
ifelse(NA, 1, "no")
```

If the value in the test vector is TRUE (or coerced to such), it returns and first element. If it is FALSE, the second. If it's neither, it returns a missing value (NA).

2.

```{r}
x <- 1:10
length(x)
as.logical(length(x))
if (length(x)) "not empty" else "empty"

x <- numeric()
length(x)
as.logical(length(x))
if (length(x)) "not empty" else "empty"
```

It works because length(x) returns a value if x is bigger than 0 that is coerced to TRUE; where if x is of 0 length, length returns 0 which is coerced to FALSE.

# 5.3. Loops

1.

```{r}
x <- numeric()
out <- vector("list", length(x))
for (i in 1:length(x)) {
  out[i] <- x[i] ^ 2
}
out
```

Because it used 1:length(x) instead of seq_along(x), so when x had length 0 the 1:length(x) went (1, 0).

```{r}
x <- numeric()
out <- vector("list", length(x))
for (i in seq_along(x)) {
  out[i] <- x[i] ^ 2
}
out
```

2.

```{r}
xs <- c(1, 2, 3)
for (x in xs) {
  xs <- c(xs, x * 2)
}
xs
```

The for loop only considers the initial xs vector, otherwise it would run forever. It only multiplies by 2 and concatenates the first three numbers.

3.
```{r}
for (i in 1:3) {
  i <- i * 2
  print(i) 
}
```

That despite i being updated inside the for loop, the intrinsic value does not change, and it continues to go according to follow the values in the initial vector given to for. Otherwise it would be 2, 4, 16