---
title: "Chapter_4_GFG"
output: 
  html_document: 
    keep_md: yes
date: "2022-10-30"
---

## 4.1. QUIZ

1. 

- With positive integers: select the element in the positions indicated by the integer.
- With negative integers: select all elements but the ones in the positions indicated by the integer.
- With logical vector: select element in the TRUE positions (if smaller than vector the logical vector is repeated until covering the entire vector).
- With character vector: select element based on their name.

2.

- [] returns a list.
- [[]] returns a vector.
- $ returns a vector.

3.

When you do not want to lose dimensions when subsetting a matrix or data frame. This is automatic in tibbles.

4.

x[]<-0 makes all elements in the matrix become 0.
x<-0 turns the matrix into a 0.

5.

```{r}
c(x = 1, y = 2, z = 3)[c("y", "z", "x")]
```

## EXERCISES

# 4.2. Selecting multiple elements

1.

```{r}
mtcars[mtcars$cyl == 4, ]
```

```{r}
mtcars[-c(1:4), ]
```

```{r}
mtcars[mtcars$cyl <= 5, ]
```

```{r}
mtcars[mtcars$cyl == 4 | mtcars$cyl == 6, ]
```

2.

```{r}
x <- 1:5
x[NA]
x[NA_real_]
```

It yields five missing values because NA is a logical by default.

3.

```{r}
x <- outer(1:5, 1:5, FUN = "*")
upper.tri(x)
x[upper.tri(x)]
```

4.

```{r}
mtcars[1:20,]
```
It returns an error because there is only 11 columns, so you cannot select 20. When using the comma you are actually selecting the first 20 rows and all columns.

5.

```{r}
x
diag(x)
```
```{r}
my_diag<-function(matrix)
{
  result<-c()
  for(i in 1:nrow(matrix))
  {
    for(j in 1:ncol(matrix))
    {
      if(i == j)
      {
        result<-c(result,matrix[i,j])
      }
    }
  }
  return(result)
}
my_diag(x)
```

6.

```{r}
df<-data.frame(a = 1:2, b = c(NA,NA))
df
df[is.na(df)] <- 0
df
```

It converts NAs into 0s, by first getting the positions of the NAs and then subsetting the data frame with this positions to convert to 0s.

# 4.3. Selecting a single element

1.

```{r}
mtcars[[3,2]]
mtcars[3,2]
mtcars[[3,"cyl"]]
mtcars[3,"cyl"]
mtcars$cyl[3]
mtcars$cyl[[3]]
mtcars[["cyl"]][3]
mtcars[["cyl"]][[3]]
```

2.

```{r}
mod <- lm(mpg ~ wt, data = mtcars)
str(mod)
mod$df.residual
summary<-summary(mod)
str(summary)
summary$r.squared
```

# 4.5. Applications

1.

```{r}
df <- data.frame(x = 1:5, y = 5:1, z = letters[1:5])
df[sample(nrow(df)),]
df[,sample(ncol(df))]
df[sample(nrow(df)),sample(ncol(df))]
```

2.

```{r}
df <- data.frame(x = 1:20, y = 20:1, z = letters[1:20])
m=5
df[sample(nrow(df),m),]
s<-sample((nrow(df)-m+1),1)
df[s:(s+m-1),drop=F]
```

3.

```{r}
df <- data.frame(y = 1:20, a = 20:1, y = letters[1:20])
df[,order(colnames(df))]
df[,sort(colnames(df))]
```

